HGP analysis

### 2019-03-02 rick/1KGP.Rmd
update

get_data <- function(loci){

@@

  data <- t(as.matrix(data[,loci]))

@@

  data <- get_data(loci)
  data_list <- get_af_data(data)

@@

  data_list <- 
    data_list %>%
  #slice(1:10) %>%
  transmute(
    locus=locus,
    fit1 = future_map(dataset, fit_model))  %>%
  transmute(
    locus=locus,
    stats = future_map(fit1, c(1)),
    predicted =future_map(fit1, c(2))) %>%
    unnest(stats) %>%
    mutate(plotted= future_map(predicted, get_plot)) %>%
    arrange(-deviance)

@@

```{r}
data_list <- run_workflow (loci=c(1:100))
data_list
```

@@

```{r}
data_list_subset %>%
  filter(locus %in% target_loci )%>%
  pull(plotted)
```

>>>>

get_data <- function(){

@@

@@

  data <- get_data()
  data <- t(as.matrix(data[,loci]))
  data_list <- get_af_data(data)

@@

  data_list <- 
    data_list %>%
  slice(1:10) %>%
  transmute(
    locus=locus,
    fit1 = future_map(dataset, fit_model))  %>%
  transmute(
    locus=locus,
    stats = future_map(fit1, c(1)),
    predicted =future_map(fit1, c(2))) %>%
    unnest(stats) %>%
    arrange(-deviance)

@@

```{r}
data_list <- run_workflow (loci=c(1:50000))
data_list
```

@@

```{r}
data_list_subset <- 
  data_list %>%
   filter(locus %in% target_loci ) %>%
    mutate(plotted= future_map(predicted, get_plot)) 
```

```{r}
data_list_subset %>%
  pull(plotted)
```
